Compilation With Program Synthesis

### 2023-08-21 new-paper/paper.tex
remove unnecessary parentheses
summarize section

\begin{lstlisting}
synth append :
  (s == (s1 ++ s2))
    ;;
  Sll @s1 -> Sll @s2 -> Sll @s;
\end{lstlisting}

>>>>

\begin{lstlisting}
synth append :
  s == s1 ++ s2
    ;;
  Sll @s1 -> Sll @s2 -> Sll @s;
\end{lstlisting}

\noindent
Using this feature, we can use \SuSLik{} specifically for \textit{synthesis} tasks inside \Pika. That is, we are able to directly use \SuSLik{} for its intended purpose.
